Neural Network Language Models for Automatic Speech Recognition

### 2018-12-10 paper/paper.tex
paper: Add section on regularization and dropout

@@

>>>>

The Milkolov paper flags that performance on the validation could not be
improved by using "standard regularization procedures" (we assume that
the paper must have been referring to L1 or L2 regualrization based on the
techniques in existence at the time) \cite{Milkolov10}. We propose that a
popular regularization technique known as "Dropout" may be of some assitance.

@@

Dropout \cite{hinton2012} is the probabilistic approximation of an ensemble
of the power-set of weights in a Neural Network. In the words of Hinton, it
reduces overfitting by reducing "complex co-adaptations on the training data",
meaning that the network does not depend too much on the activation of
certain sets of units in order to produce the majority of activations, instead
ensuring that every unit is utilized roughly equally. In the case of language models,
this should in principle prevent the network from just recalling the training data.
